01_pca

### 2019-05-29 analysis/02_pca_all.Rmd
umm, two days old commits

p <- autoplot(pca, data = samples, alpha = 'tissue', shape = "sex")
p

edgRpca12 <- p + labs(subtitle = "Normalized counts from edgeR") +
  scale_alpha_discrete(name = "tissue", labels = c("hypothalamus", "pituitary", "gonad")) +
  scale_shape_discrete(name = "sex", labels = c("female", "male")) +
  #xlab(stringr::str_replace(p$labels$x, "PC", "Principle Component ")) +
  #ylab(stringr::str_replace(p$labels$y, "PC", "Principle Component ")) +
  theme_rmh() + guides(alpha = guide_legend(order = 1), 
              shape = guide_legend(order = 2)) +
  stat_ellipse(aes(linetype = sex, colour = tissue))
edgRpca12
```

@@

## sex and timepoint within a tissue

```{r timepointsex}
plotlist = list()
for (eachtissue in levels(samples$tissue)){

  print(eachtissue)

  colData <- samples %>%
      dplyr::filter(tissue == eachtissue) %>%
      droplevels()
  row.names(colData) <- colData$V1

  savecols <- as.character(colData$V1) 
  savecols <- as.vector(savecols)

  countData <- counts %>% dplyr::select(one_of(savecols))

  # check that row and col lenghts are equal
  print(ncol(countData) == nrow(colData))

  pca <- prcomp(t(countData))

  p <- autoplot(pca, data = colData, fill = lastday, color = penultimate, shape = "tissue")

en <- p + labs(subtitle = eachtissue) +
  theme_rmh() +  guides(color = guide_legend(order = 1), 
              shape = guide_legend(order = 2)) +
  theme_bw(base_size=8) +
    theme(legend.position = "bottom") + 
  scale_fill_manual(values = colorlastday) +
  scale_color_manual(values = colorpenultimate)

legend <- get_legend(en)

en <- en  + theme(legend.position = "none")

plotlist[[eachtissue]] = en

#plot(en) 
}

main <- grid.arrange(grobs=plotlist,ncol=3)

withlegend <- plot_grid( main, legend, rel_heights  = c(3, .3), ncol = 1)
withlegend

>>>>

p <- autoplot(pca, data = samples, colour = 'tissue', shape = "sex")
p

edgRpca12 <- p + labs(subtitle = "Normalized counts from edgeR") +
  scale_colour_discrete(name = "tissue", labels = c("hypothalamus", "pituitary", "gonad")) +
  scale_shape_manual(name = "sex", labels = c("female", "male"), values = c(21,19)) +
  theme_rmh() + guides(color = guide_legend(order = 1), 
              shape = guide_legend(order = 2)) +
  stat_ellipse(aes(linetype = sex, colour = tissue))
edgRpca12
```

@@
